%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Andrew Kuksov} % Your name
\address{\underline{\href{https://github.com/3mph4515}{Github}} \\ \underline{\href{https://www.linkedin.com/in/makelovenotwar/}{LinkedIn}}}
\address{Warsaw, Poland \\ Minsk, Belarus} % Your address
\address{+48730390964 \\ andrei.kuksow@gmail.com \\ Warsaw, Poland} % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%   PROFILE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Profile}
Talented Android Developer with over eight years of software development experience in a broad
range of industries. Solid understanding of full mobile development life cycle, UX/UI, Analytics. Dedicated to continuously developing, implementing, and adopting new technologies to maximize development efficiency and produce innovative applications. Always open to challenges and new opportunities.\\
My english level is \textbf{B2(Upper intermediate)}.

\end{rSection}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Belarusian State University of Informatics and Radioelectronics, Minsk} \hfill {\em July 2015} \\ 
Faculty of Computer Systems and Networks \\
B.S. in Systems Engineering \\

\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNOLOGY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Have experience with}
Kotlin, Java, RxJava, DI (Dagger 2/Hilt), Coroutines, Clean Architecture, MVP/MVVM/MVI, Networking (OkHttp, Retrofit), Multitasking, Connectivity, Bluetooth LE, Google Maps, Google Play Billing, FCM, Android Architecture Components, UI components, Animation, Custom Views, Geofence.

\end{rSection}


%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work positions}

\begin{rSubsection}{Appsyoulove(LiftApp)}{April 2021 - Present}{Android Software Engineer}{Minsk, Belarus - Warsaw, Poland, remote}
\item[]Worked on a mobile games written with pure Android SDK.\smallskip \\
\textbf{Numberzilla}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=com.appcraft.number.puzzle&hl=en}{Link to Google Play}}\\
\textbf{Catris}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=com.appcraft.merge.game&hl=en}{Link to Google Play}}
\item Analyzed estimated and developed new game features and improved the old ones. Improved and keep the crash-free rate at 99.9\%
\item Code health improvements (code reviews, eliminating tech debt, refactoring).
\item Application health improvements(decreased application start-up time, profiled FPS drops) Communicated with advertisement 3-rd party SDK team to report and fix SDK issues. 
\item Built in ANR-watchdog library to collect and investigate roots of the issues to decrease ANR ratio of application.
\item Worked a lot with animations, custom views, graphics so started to pay huge attention to small details in my future apps.
\item Started experimenting with Jetpack Compose and wrote a small mini-game with Compose.
\item Fully re-factored large project and migrated from Kotlin synthetics to Jetpack view binding.
\item Wrote Unit test to cover game core logic.
\item Participated in application feedback analysis, helped users to solve their issues as well did enhancement based on users' reviews and feedback.
\end{rSubsection}


\begin{rSubsection}{Pixolio}{September 2019 - April 2021}{Android Software Engineer}{Minsk, Belarus}
\item[] Worked in product company on food-delivery ecosystem. Participated in creating from scratch application for food order(users), food delivery(couriers), orders management(restaurants) in a team consists of 3 Android Developers.\smallskip \\
\textbf{Scope Delivery}\hspace{15mm}\underline{\href{https://play.google.com/store/apps/details?id=city.scope.delivery}{Link to Google Play}}\hspace{15mm}
\textbf{Scope Bussines}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=city.scope.biz}{Link to Google Play}}\\
\textbf{Scope Guides}\hspace{18mm}\underline{\href{https://play.google.com/store/apps/details?id=city.scope}{Link to Google Play}}\hspace{15mm}
\textbf{Scope Employee}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=city.scope.employee}{Link to Google Play}}
\item Contributed to the full development lifecycle of mobile phone applications from planning,
Requirements gathering, development, testing, launching, and porting, to maintenance/code
enhancement.
\item Designed UI using views provided by Android and created custom views when required
\item Built cool, modern application for food-order inspired by Uber Eats, Bolt Food, Yandex Eda, Wolt. Combine best patterns to achieve smooth user experience. 
\item Implemented a lot of server-driven UI, AB-tests. Used self-made solution for strings localization. It was possible to update translations and text without application re-submit to Google Play.
\item Created many in-house libraries and scripts to speed up development(Auth, FCM, Navigation, Maps, Networking, Localization and Settings, etc. were moved to base modules and reused in every application).
\item Implemented all the payment options via payment gateway.
\item Set-up build scripts to produce test and production builds, CI/CD with Github Actions.


\end{rSubsection}


\begin{rSubsection}{Helmes}{February 2019 - September 2019}{Android Software Engineer}{Minsk, Belarus}
\item[] Worked in a multi-national team of 9 Android developers across Belarus/the USA/Switzerland on application which was aimed to allow users to manage and interact with their vehicles digitally. Users can easily share a vehicle damage report with the insurance company and simplify all processes related to the registration the vehicle damage in the insurance company.\smallskip \\


\item Worked in different phases of project life cycle like design, development and testing of application for Android mobile devices.
\item Involved in requirement gathering, UI design and development.
\item Responsible for design of user interface using various custom layouts, buttons, dialog boxes, alert boxes and edit boxes.
\item Regularly did code reviews
\end{rSubsection}



\begin{rSubsection}{Intellectsoft}{February 2016 - February 2019}{Android Software Engineer}{Minsk, Belarus}
\item[] Worked on a huge amount of different projects. Creating them from scratch, support existing, re-factoring. \smallskip \\
Most noticeable:\smallskip \\
\textbf{Adero}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=com.adero.app}{Link to Google Play}}\\
Adero’s two-part system comprises smart tags and “taglets.” The former adhere to bags, carry-on bags, backpacks, gym bags, and containers, while the latter stick to items stowed inside of those packs, such as wipes, headphones, laptops, and passports. The smart tags communicate with taglets and alert users through Adero’s smartphone app via a notification when they accidentally leave something important behind. \textbf\hfill\underline{\href{https://venturebeat.com/ai/adero-formerly-trackr-launches-new-smart-tag-system-with-proactive-notifications/}{Press about it}}
\item Worked in a team of 4 Android developers
\item Worked in a multi-national team across USA/Sweden/Ukraine
\item Architecture planning and implementation
\item Functionality implementation
\item UX aspects discussion
\item Profiling, code optimization
\item Unit testing
\item Used the Bluetooth APIs to connect and communicate with custom devices. 
\item Participated in interviewing potential candidates
\item Have been helping with onboarding of new team members\\
\textbf{Health-care inventory application}\\
The application is for internal use only inside hospitals. The main idea of the project is the simplification of inventory inside buildings. The application connects to two devices: printer and RFID wand. From the application, you can print RFID tags on a special printer. With RFID wand, you can scan the area around you and check out the devices found in the application. accidentally leave something important behind.
\item Architecture planning and implementation
\item Functionality implementation
\item UX aspects discussion
\item Custom Components


\end{rSubsection}


\begin{rSubsection}{J-lab}{November 2013 - February 2016}{Android Software Engineer}{Minsk, Belarus}
\item[] My first workplace where I started learning Android Development staff and worked with Android 2.4+, Sherlock ActionBar, AsyncTask, Volleys and another staff that's nobody knows in  a modern Android world. But one of my project is still exists and reachable in Google Play: \smallskip \\
\textbf{Callisto Mobile}  \hfill\underline{\href{https://play.google.com/store/apps/details?id=com.jerminal.callistomobile}{Link to Google Play}}\\
An application for security guards that helps to make rounds and fill out reports, take pictures.\\

\item Got knowledge in Web Services, JSON, Android Studio, Eclipse IDE, SQLite database,
Activities, Services, Broadcast Receivers, UI Designing. 
\item Used Web Services and networking to parse JSON online data from server.
\item Integrated location-based services using Google Maps API
\item Designed and developed the request and response data to and from database.
\item Developed and implemented custom Layouts, Views, AsyncTasks, Adapters, Lists, Fragments and more.
\end{rSubsection}



\end{rSection}

%----------------------------------------------------------------------------------------
%   NOTES SECTION

%\begin{rSection}{Some facts to better understand what kind of person I am}
%  \smallskip
%  \begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
%    \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics  
%  \item I decided to tie my work to computers when I was 5.
%  \item First program was in Pascal at 13.
%  \item I'm fond of playing tennis, snowboarding, jogging.
%  \end{list}
%\end{rSection}
%----------------------------------------------------------------------------------------

\end{document}
